---
title: "MT Cars Shiny Pitch"
author: "Mike Finch"
date: "7/30/2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
```

## Overview

This is the manual for an application that can be found [here](https://gamecock.shinyapps.io/CourseraHomework/), with source in [Github](https://github.com/Gamecock/CourseraDataProducts).
The application provides various ways of looking at the mtcars dataset.


>The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

The y axis is fixed at MPG, however the x-axis color and marker can be selected from a number of other variables.

## Sample Plot

```{r pressure}
data("mtcars")
g <- ggplot( data = mtcars, y = mpg, x = disp, aes( disp, mpg)) + geom_point()
g
```


## Color and Marker Choices

- Cylinders(cyl)
- V or Straight engine(vs, 0 = V, 1 = Straight)
- Automatic or Manual Transmission(am, 0 = Automatic, 1 = Manual)
- Number of Forward Gears(gear)
- Number of Carburators(carb)

## X-axis Choices

- Displacement(disp)
- Horsepower(hp)
- 1/4 Mile Time(qsec)
- Weight(wt)


